### 2018-01-25 thermocouple/paper.tex
Added abstract

	Abstract goes here

@@

>>>>

	In this experiment the EMF across a thermocouple was measured at a variety of temperatures to invesigate the Seebeck Effect. Plotting the obtained data on a calibration curve proved the expected linear relationship. Upon fitting the temperature differences to the potential using the least squares method, the Seebeck coefficient was determined to be \( \pars{0.0410 \pm 0.0003} \si{\milli\volt\per\kelvin} \). Further, the resistance of the thermocouple was measured to be $(1.8\pm.4)\si{\ohm}$.

@@

	EMF generated along the conductor is quantified by the Seebeck Effect, a proportionality law relating the potential and the temperature difference.
	\papereq{Seebeck}{V = S\pars{T_1 - T_2}}{Serbanescu}
	\begin{paperwhere}
		\papervar{S}{Seebeck coefficient}{\volt\per\kelvin}
		\papervar{T_1}{absolute temperature at first junction}{\kelvin}
		\papervar{T_2}{absolute temperature at second junction}{\kelvin}
	\end{paperwhere}

	The experiment setup included a multimeter acting as a voltmeter, two thermal flasks to ensure that the temperature was kept constant and a thermometer all arranged as shown below.

	\paperfig{setup}{\pdf{setup}}{}
